Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame

### 2023-01-11 manuscript/Chapter2-manuscript.Rmd
some updates based on PO's comments.

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021]. Indeed, predator populations often comprise assemblages of individuals specializing in different foraging strategies or resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017]. A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, can be major drivers of such individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016]. When they hunt, predators often use techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e. experience). While hunting experience may be essential to maintain or improve foraging success, we have have limited evidence for either its role in predator foraging specialization or the ecological/fitness consequences of such among individual behavioural differences on predator-prey interactions [@Dukas2019].

The integration of individual behavioural variation in the study of predator-prey interactions has gained traction in recent years, with empirical studies revealing important consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a]. However, an important and recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey. We recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can overcome this challenge, and uncover details of the mechanisms shaping these interactions [@FraserFranco.etal2022]. For instance, we found that the classical locomotor crossover hypothesis [@Huey.Pianka1981] applied only for cursorial hunters [see also: @Matsumura.Miyatake2022a], suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research. Other studies on virtual predator-prey systems show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al. in prep). Because virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization along with its potential fitness consequences.

@@

There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging (REFERENCES). Importantly, we have limited information on the ecological contexts - except for competition - that favour one strategy over the other. This is reflected in the literature showing contrasting results in the links between specialization and fitness. For instance, some studies report increasing benefits of specialization [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015]. While quantifying the fitness consequences of specialization is a daunting task, in predator-prey systems, some clues indicate that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018]. The resource-predictability hypothesis argues that when resources are predictable, individual specialists should have higher delivery rates by reducing the energy and time required to search for and handle prey. In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019]. This hypothesis has, however, not been tested in systems where behavioural interactions are simultaneously monitored between predator and prey individuals.

In this study, we analyze individual behavioural data from players in *Dead by Daylight* (*DBD*) to test how hunting experience and prey behaviour shape predator foraging specialization. *DBD* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments. The data grants a high degree of precision on the behavioural interaction as both the predator and the four prey are measured simultaneously in each trial. First, we investigate how predators developed their individual hunting expertise. We hypothesize that predators should differ in the development of their expertise because they encounter varying levels of difficulty with the prey that they pursue. Second, we test the hypothesis that individual variation in foraging behaviour will change with experience. If experience reduces the costs of switching between hunting tactics, we predict that individual predators should become more flexible with time. Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize. Third, we evaluate how predator foraging specialization interacts with variation in prey behaviour. Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize when encounters are less predictable. Lastly, if individuals differ in their degree of foraging specialization, then we expect specialist hunters to fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.

@@

*DBD* is a survival asymmetric multiplayer online game developed by Behaviour Interactive Inc. In this game, players get to choose if they wish to play as a predator or a prey. The objective of the predator-player is to hunt and capture the four prey players across a virtual environment. The objective of the four prey players is to forage for resources while avoiding the predator. The resources are in the form of power generators that, once activated, will enable the prey to escape through one of two exit doors. The composition of the predator and prey group for a match is determined by a skill-based matchmaking algorithm. A match ends when the predator kills all the prey available (i.e. that have not escaped), or when the last remaining prey escapes the virtual environment. Each player, predator or prey, can choose an avatar with abilities that encourage specific play styles (e.g. bold vs cautious prey, or ambush vs roaming predator). During our study period, the game offered 23 playable predator avatars. The virtual environment where matches take place is composed of fixed and procedurally generated habitat components, such as vegetation, mazes, and buildings. Some of these environments are larger than others, with varying structural complexity. However, we have previously shown that predators display only minimal changes in behaviour and hunting success across the environments, probably due to a game feature enabling predators to have visual cues of the generators [@FraserFranco.etal2022]. There were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for play during our study period.

Individual predators in *DBD* display variation in the hunting strategies that they use. Some specialize at hunting at high speeds and covering space in the environment, while others prefer to stalk and ambush their prey [@FraserFranco.etal2022]. They also display flexibility in the use of these tactics by switching between them across matches. The expression of these tactics and their success is also shaped by the behaviour of the prey group. The prey need to forage for resources while paying attention to the predator to avoid being detected and chased. Some prey contribute to the group's success by healing or helping others escape the predator, while others play alone and attempt to escape by themselves [@Cere.etal2021]. Predators must be wary of how the prey behave to choose the right way to capture them. Thus, *DBD* simulates a highly dynamic system where both predators and prey must constantly adjust to each other to be successful.

@@

The videogame company provided data that spanned a period of 6 months of gameplay recorded for every player. The first recorded match was played on `r toString(format(min(dat$date)))`, and the last one on `r toString(format(max(dat$date)))`. We cleaned and filtered the raw data to produce a dataset appropriate for our analyses. We analyzed only matches where players did not know each other (i.e. "Online" mode). We filtered any matches where players were inactive, such as when speed values were equal to, or very close to, zero. Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game has it is supposed to be played. We then partitioned the player population by total experience, and sampled players that played 300 matches or more. To optimize the representation of gameplay experience at advanced levels, we set the maximum number of matches at 500 for these players. For instance, there could be a large difference in gameplay between 300-500 and 500-1000 matches. Players that played above 500 matches represented only ~2% of the population.

@@

We analyzed the predator's average speed and the average speed of the prey encountered by the predator. The predator's average speed is measured as the average distance per second traveled during a match ($\overline{x}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`). For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group ($\overline{x}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))`). Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`). Lastly, the predator's cumulative experience was defined as the number of matches played prior to the match being monitored. For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9.

@@

We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience. We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated variance ($id \sim N(0,\ I\ \sigma^2_{id})$). We defined all models to run four MCMC chains with 1000 posterior samples for each parameter. To do so, we ran 2500 iterations for the first model with a thinning set to eight, and 1500 iterations with a thinning set to four for the second and third models; burn-in was set to 500 iterations in each model. We provide a description of how we specified the priors for each model in the supporting information. After fitting the three models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].

@@

where $env \sim N(0,\ I\ \sigma^2_{env})$, $av \sim N(0,\ I\ \sigma^2_{av})$, and $id \sim N(0,\ I\ \sigma^2_{id})$. $b$ is the vector of fixed effects with its incidence matrix $X$. $env$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their incidence matrices $M$, $N$, and $Z$. The variance parameters $\sigma^2_{env}$, $\sigma^2_{av}$, and $\sigma^2_{id}$, correspond to the among environment, among avatar, and among individual variances, respectively. $I$ is the identity matrix, with $I\sigma^2$ indicating that the random effects are independently and identically distributed. The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively. Equations (1) and (2) were parametrized with a Gaussian distribution family (predator and prey speed), while equation (3) was parametrized with a beta-binomial distribution family (predator hunting success). We parametrized the model to run four MCMC chains with 1000 posterior samples for each parameter. To do so, we ran 2500 iterations with a thinning set to 8, with the first 500 iterations used as warmups. We explain how we specified the priors of the MDHGLM in the supporting information.

We estimated the correlation between the individual random effect on the mean and on the dispersion within each trait (e.g. $cor(\sigma^2_{id_{m}\ pred}\ \sigma^2_{id_{d}\ pred})$) and among each trait (e.g. $cor(\sigma^2_{id_{m}\ pred}\ \sigma^2_{id_{d}\ prey})$) within a level of experience. We also evaluated these correlations among the different levels of experience (e.g. $cor(\sigma^2_{id_{m}\ pred\ novice}\ \sigma^2_{id_{d}\ pred\ intermediate})$). The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each developmental stage. The correlations were estimated using a multivariate Gaussian distribution.

@@

Contrary to our predictions, we detected only minimal differences in movement speed among individual predators, and these differences did not change with experience (Figure 2A). However, individuals differed in their degree of flexibility, and these differences tended to increase, yet marginally, with experience (Figure 2B). Overall, individual predators appeared to have encountered prey with similar average speeds (Figure 2A), and our results do not support our prediction that predators would encounter prey with varying levels of speed (Figure 2B).

@@

At all experience levels, predators that were on average faster were also travelling faster in all their matches (i.e. they were more specialized at travelling fast). Thus, slower predators were also more flexible in their movement through time (Figure 4). This pattern became stronger as predators gained experience (Figure 4). In general, predators tended to be faster and also more specialized in this strategy when they encountered prey that were on average faster (Figure 4). Moreover, predators favored and specialized in a faster foraging mode when encounters with prey were more predictable, and these relationships also became stronger with experience (Figure 4).

>>>>

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021]. Indeed, predator populations often comprise assemblages of individuals specializing in different foraging strategies or resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017]. A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, can be major drivers of such individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016]. When they hunt, predators often use techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e. experience). While hunting experience may be essential to maintain or improve foraging success, we have limited empirical assessments of its role in predator foraging specialization [@Dukas2019], nor its consequences on predator-prey interactions.

The integration of individual behavioural variation in the study of predator-prey interactions has gained traction in recent years, with empirical studies revealing important consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a]. However, an important and recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey. We recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can overcome this challenge and help uncovering the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022]. For instance, we found that the classical locomotor crossover hypothesis [@Huey.Pianka1981] applied only for cursorial hunters [see also: @Matsumura.Miyatake2022a], suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research. Other studies on virtual predator-prey systems show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al. in prep). Because virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization along with its potential fitness consequences.

@@

There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging (REFERENCES). Importantly, we have limited information on the ecological contexts - except for competition - that favour one strategy over the other. This is reflected in the literature showing contrasting results in the links between specialization and fitness. For instance, some studies report increasing benefits of specialization [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015]. While quantifying the fitness consequences of specialization is a daunting task, in predator-prey systems, some clues indicate that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018]. The resource-predictability hypothesis argues that when resources are predictable, individual specialists should have higher delivery rates by reducing the energy and time required to search for and handle prey. In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019]. This hypothesis has, however, not been tested in systems where behavioural interactions are simultaneously monitored between predator and prey individuals. Thus, uncovering the mechanisms shaping direct predator-prey interactions would enable researchers to better predict the behavioural decisions of predators when they are hunting.

In this study, we analyze individual behavioural data from players in *Dead by Daylight* (*DBD*) to test how hunting experience and prey behaviour shape predator foraging specialization. *DBD* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments. The data grants a high degree of precision on the behavioural interaction as the behaviour of both the predator and the four prey is monitored simultaneously in each trial. First, we investigate how predators develop their individual hunting expertise. We hypothesize that predators should differ in the development of their expertise because they encounter varying levels of difficulty with the prey that they pursue. For example, a predator may face more difficulty than other individuals if it encountered prey that were more elusive. Second, we test the hypothesis that individual variation in foraging behaviour will change with experience. If experience reduces the costs of switching between hunting tactics, we predict that individual predators should become more flexible with time. Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize. Third, we evaluate how predator foraging specialization interacts with variation in prey behaviour. Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize when encounters are less predictable. Lastly, if individuals differ in their degree of foraging specialization, then we expect specialized hunters to fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.

@@

*DBD* is a survival asymmetric multiplayer online game developed by Behaviour Interactive Inc. In this game, players can play as a predator or a prey. The objective of the predator is to hunt and capture the four prey across a virtual environment. The objective of the four prey is to forage for resources while avoiding the predator. The resources are in the form of power generators that, once they are all activated, will enable the prey to escape through one of two exit doors. The composition of the predator and prey group for a match is determined by a skill-based matchmaking algorithm. A match ends when the predator kills all the prey available (i.e. that have not escaped), or when the last remaining prey escapes the virtual environment. Each player, predator or prey, can choose an avatar with abilities that encourage specific play styles (e.g. bold vs cautious prey, or ambush vs roaming predator). During our study period, the game offered 23 predator avatars. The virtual environment where matches take place is composed of fixed and procedurally generated habitat components, such as vegetation, mazes, and buildings. Some of these environments are larger than others, with varying structural complexity. However, we have previously shown that predators display only minimal changes in behaviour and hunting success across the environments, probably due to a game feature enabling predators to have visual cues of the generators [@FraserFranco.etal2022]. There were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for play during our study period.

In *DBD*, some individual predators specialize on hunting at high speeds and covering space in the environment, while others prefer to stalk and ambush their prey [@FraserFranco.etal2022]. Individuals are also flexible in the use of these tactics by switching between them across matches. The expression of these tactics and their success is also shaped by the behaviour of the prey group. The prey need to forage for resources while paying attention to the predator to avoid being detected and chased. Some prey contribute to the group's success by healing or helping others escape the predator, while others play alone and attempt to escape by themselves [@Cere.etal2021]. Predators must be wary of how the prey behave to choose the right way to capture them. Thus, *DBD* simulates a highly dynamic system where both predators and prey must constantly adjust to each other to be successful.

@@

The videogame company provided data that spanned a period of 6 months of gameplay recorded for every player. The first recorded match was played on `r toString(format(min(dat$date)))`, and the last one on `r toString(format(max(dat$date)))`. We cleaned and filtered the raw data to produce a dataset appropriate for our analyses. We analyzed only matches where players did not know each other (i.e. "Online" mode). We filtered any matches where players were inactive, such as when speed values were equal to, or very close to, zero. Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game has it is supposed to be played. We then partitioned the player population by total experience, and sampled players that played 300 matches or more. To optimize the representation of gameplay experience at advanced levels, we set the maximum number of matches at 500 for these players. For instance, there could be a large difference in gameplay between 300-500 and 500-1000 matches. Players that played above 500 matches represented ~2% of the population.

@@

We analyzed the predator's average speed and the average speed of the prey encountered by the predator. The predator's average speed is measured as the average distance traveled per second during a match ($\overline{x}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`). We measured the preys' average speed as the average travel speed of the four individual prey within a match ($\overline{x}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))`). We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`). Lastly, we defined the predator's cumulative experience as the number of matches played prior to the match being monitored. For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9.

@@

We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience. We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated variance ($id \sim N(0,\ I\ \sigma^2_{id})$). We estimated the parameters in all models using four MCMC chains with 1000 posterior samples for each parameter. To do so, we ran 2500 iterations for the first model with a thinning set to eight, and 1500 iterations with a thinning set to four for the second and third models; burn-in was set to 500 iterations in each model. We provide a description of how we specified the priors for each model in the supporting information. After fitting the three models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].

@@

where $env$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their incidence matrices $M$, $N$, and $Z$. $b$ is the vector of fixed effects with its incidence matrix $X$. The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively. We assumed that all random effects followed a Gaussian distribution with estimated variance ($env \sim N(0,\ I\ \sigma^2_{env})$, $av \sim N(0,\ I\ \sigma^2_{av})$, and $id \sim N(0,\ I\ \sigma^2_{id})$). The variance parameters $\sigma^2_{env}$, $\sigma^2_{av}$, and $\sigma^2_{id}$, correspond to the among environment, among avatar, and among individual variances, respectively. $I$ is the identity matrix, with $I\sigma^2$ indicating that the random effects are independently and identically distributed. Here, we assume that the residuals vary among individuals where $e \sim N(0,\ Diag\ [\sigma^2_{e}])$, $[\frac{id_m}{id_v}] \sim N\left(\begin{array}{cc} 0 \\ \\ 0 \end{array},\ \Sigma_{id} \otimes\ I \right)$, and $\Sigma_{id}$ is a variance covariance matrix of the individual identity random effect. Equations (1) and (2) were parametrized with a Gaussian distribution family (predator and prey speed), while equation (3) was parametrized with a beta-binomial distribution family (predator hunting success). We parametrized the model to run four MCMC chains with 1000 posterior samples for each parameter. To do so, we ran 2500 iterations with a thinning set to 8, with the first 500 iterations used as warmups. We explain how we specified the priors of the MDHGLM in the supporting information.

We estimated the correlation between the individual random effect on the mean and on the dispersion within each trait (e.g. $cor(\sigma^2_{id_{m}\ pred}\ \sigma^2_{id_{d}\ pred})$) and among each trait (e.g. $cor(\sigma^2_{id_{m}\ pred}\ \sigma^2_{id_{d}\ prey})$) within a level of experience. In the first case, this allows us to assess, for example, whether predators that are on average slower/faster are more specialized or flexible. In the second case, the correlations enables us to estimate, for example, whether slower/faster (or more specialized/flexible) predators encountered prey that were faster/slower, or if slower/faster predators had lower/greater hunting success. We also evaluated these correlations among the different levels of experience (e.g. $cor(\sigma^2_{id_{m}\ pred\ novice}\ \sigma^2_{id_{d}\ pred\ intermediate})$). The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each developmental stage. The correlations were estimated assuming a multivariate Gaussian distribution.

@@

Contrary to our predictions, we detected only minimal differences in movement speed among individual predators, and these differences did not change with experience (Figure 2A). However, individuals differed in their degree of flexibility, and these differences increased marginally with experience (Figure 2B). Overall, individual predators encountered prey with similar average speeds (Figure 2A), and our results do not support our prediction that predators would encounter prey with varying levels of speed (Figure 2B).

@@

# =======================================================================

# Extract the correlations to report values in the text

# =======================================================================

# =======================================================================
# Prepare the draws
# =======================================================================

 # Model
 path <- here::here("outputs", "02_outputs_models")
 fit <- readRDS(file.path(path, "02B_DHMLM.rds"))

 # Extract te draws
 draws <- data.table(
     as_draws_df(
         fit,
         variable = c("cor"),
         regex = TRUE)
 )

 draws[, c(106:109) := NULL]

 # =======================================================================
 # =======================================================================

 # =======================================================================
# 2. Transform the draws table
# =======================================================================

# Reshape the table -----------------------------------------------------

 # Long format
 table <- melt(draws,
               measure = patterns("^cor_predator_id"),
               variable.name = "correlation")

 # Summarize the values (means + 95% CI) ---------------------------------

 # Intervals
 lower_interval <- function (x) {coda::HPDinterval(as.mcmc(x), 0.95)[1]}
 upper_interval <- function (x) {coda::HPDinterval(as.mcmc(x), 0.95)[2]}

 table[, ":=" (mean = mean(value),
               lower_ci = lower_interval(value),
               upper_ci = upper_interval(value)),
       by = .(correlation)]

 cor_tab <- unique(table[, c(1, 3:5)])

 # Round values to 3 digits
 cor_tab[, c(2:4) := lapply(.SD, function (x) {round(x, digits = 3)}),
         .SDcols = c(2:4)]

# =======================================================================
# =======================================================================

At all experience levels, predators that were on average faster were also travelling faster in all their matches ($cor_{novice}$ = `r toString(format(cor_tab[1,2]))` [`r toString(format(cor_tab[1,3]))`, `r toString(format(cor_tab[1,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[6,2]))` [`r toString(format(cor_tab[6,3]))`, `r toString(format(cor_tab[6,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[15,2]))` [`r toString(format(cor_tab[15,3]))`, `r toString(format(cor_tab[15,4]))`]) (i.e. they were more specialized at travelling fast). Thus, slower predators were also more flexible in their movement through time (Figure 4). This pattern became stronger as predators gained experience (Figure 4). In general, predators tended to be faster when they encountered prey that were on average faster ($cor_{novice}$, $cor_{interm}$, $cor_{adv}$) (Figure 4). They were also more specialized at being fast when prey were on average faster (Figure 4).

Moreover, predators favored and specialized in a faster foraging mode when encounters with prey were more predictable, and these relationships also became stronger with experience (Figure 4).
